---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggborderline

<!-- badges: start -->
<!-- badges: end -->

{ggborderline} provides a set of geoms to make line plots a little bit nicer. Use
this package along with [ggplot2](https://ggplot2.tidyverse.org/) to:

* Improve the clarity of line plots with many overlapping lines
* Draw more realistic worms

# Installation

You can install the development version of ggborderline from [github](https://github.com/wurli/ggborderline) with:
```r
remotes::install_github("wurli/ggborderline")
```

## Usage

Here is a very basic line plot 

```{r example}
library(ggborderline)
library(ggplot2)

# geom_borderline() adds a border around lines
ggplot(economics_long, aes(date, value01, colour = variable)) +
  geom_borderline()

# You can control the size and colour of the border with the
# border_size and border_colour aesthetics:
ggplot(economics_long, aes(date, value01, border_colour = variable)) +
  geom_borderline(border_size = .4, colour = "white")

# The background 'border' part of the geom is always solid, however this
# can be used to create some nice effects:
x <- seq(0, 4 * pi, length.out = 500)
test_data <- data.frame(
  x = rep(x, 2), y = c(sin(x), cos(x)),
  fun = rep(c("sin", "cos"), each = 500)
)

ggplot(test_data, aes(x, y, colour = fun)) +
  geom_borderline(size = 1, linetype = "dashed", lineend = "round")
```

<details>
<summary>Click here for hyper-realistic worms</summary>
```{r, echo = FALSE}
x <- seq(-1, 0.5, length.out = 500)
worm_data <- data.frame(
  x = rep(x, 2), y = c(sin(x * pi), cos(x * pi)),
  colour = rep(c("pink", "pink2"), each = 500)
)

dirt <- c("#453d30", "#453d30", "#988b77", "#856e52", "#695e48")

colours <- data.frame(
  x = runif(30000, -1.1, 0.6), y = runif(30000, -1.1, 1.1),
  colour = sample(dirt, 10000, replace = TRUE)
)

ggplot(worm_data, aes(x, y, colour = colour)) +
  geom_point(data = colours, size = 2.5, alpha = 0.8) +
  geom_borderline(size = 10, border_size = 1, border_colour = "pink3", lineend = "round") +
  scale_colour_identity() +
  theme_void() +
  theme(panel.background = element_rect(fill = "grey10")) +
  annotate(geom = "text", label = ":)", x = 0.5, y = 0:1, angle = 270, size = 6)
```
</details>

# Inspiration
I made this package after seeing this *beautiful* plot by [Rosamund Pearce](https://twitter.com/_rospearce):
<blockquote class="twitter-tweet"><p lang="en" dir="ltr">I designed my first double-page <a href="https://twitter.com/hashtag/dataviz?src=hash&amp;ref_src=twsrc%5Etfw">#dataviz</a> for The Economist!<br><br>It depicts our new &#39;Normalcy index&#39;, which tracks the world&#39;s return to pre-pandemic life &gt;&gt; <a href="https://t.co/Iko6totfJN">https://t.co/Iko6totfJN</a> <a href="https://t.co/1sIUMoZco1">pic.twitter.com/1sIUMoZco1</a></p>&mdash; Rosamund Pearce (@_rospearce) <a href="https://twitter.com/_rospearce/status/1410903833442717698?ref_src=twsrc%5Etfw">July 2, 2021</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

# Credit
This package would not have been possible without the fantastic [ggplot2](https://ggplot2.tidyverse.org/)
package, and would have been very difficult without the [accompanying book](https://ggplot2-book.org/). 
My humble and sincere thanks go to all the authors who make projects like this possible.
